ABM simulating short-term mating behaviors

### 2022-06-02 README.Rmd
minor edits to the figures
minor edits to the README file

---
title: "ABM simulating short-term mating behaviors"
author: "Yurun (Ellen) Ying"
date: "5/6/2022"
output: 
  github_document:
    html_preview: true
---

## Description
By using a spatial agent-based model, the present study investigated we investigated whether men and women's different mating preferences resulted in any gender differences in short-term mating behaviors, and if they did, under what circumstances.

```{r library_calls, message=FALSE, echo=FALSE}
library(tidyverse)
library(here)
library(broom)
library(effectsize)
library(ggplot2)
library(rmarkdown)
library(knitr)
library(kableExtra)
```

### Dependencies:
- Netlogo version 6.2.1
- `r R.version.string`
  - `tidyverse` (v. `r packageVersion("tidyverse")`)
  - `here` (v. `r packageVersion("here")`)
  - `broom` (v. `r packageVersion("broom")`)
  - `effectsize` (v. `r packageVersion("effectsize")`)
  - `ggplot2` (v. `r packageVersion("ggplot2")`)
  - `rmarkdown` (v. `r packageVersion("rmarkdown")`)
  - `knitr` (v. `r packageVersion("knitr")`)
  - `kableExtra` (v. `r packageVersion("kableExtra")`)

>>>>

---
title: "ABM simulating short-term mating behaviors"
author: "Yurun (Ellen) Ying"
date: "5/6/2022"
output: 
  github_document:
    html_preview: false
---

## Description
By using a spatial agent-based model, the present study investigated whether men and women's different mating preferences resulted in any gender differences in short-term mating behaviors, and if they did, under what circumstances.

```{r library_calls, message=FALSE, echo=FALSE}
library(tidyverse)
library(here)
library(broom)
library(effectsize)
library(rmarkdown)
library(knitr)
library(kableExtra)
```

### Dependencies:
- Netlogo version 6.2.1
- `r R.version.string`
  - `tidyverse` (v. `r packageVersion("tidyverse")`)
  - `here` (v. `r packageVersion("here")`)
  - `broom` (v. `r packageVersion("broom")`)
  - `effectsize` (v. `r packageVersion("effectsize")`)
  - `rmarkdown` (v. `r packageVersion("rmarkdown")`)
  - `knitr` (v. `r packageVersion("knitr")`)
  - `kableExtra` (v. `r packageVersion("kableExtra")`)
